---
title: "COVID19 - New Zealand"
author: "Matt Bixley"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    # social: ["facebook", "twitter", "linkedin"]
    source_code: embed
    vertical_layout: fill
---

```{r setup, include=FALSE}
#------------------ Packages ------------------
library(flexdashboard)
library(tidyverse)
library(lubridate)

#------------------ Parameters ------------------
# Set colors
# https://www.w3.org/TR/css-color-3/#svg-color
cases_color <- "black"
death_color <- "red"
#------------------ Data ------------------
jhu_confirmed <- paste("https://raw.githubusercontent.com/CSSEGISandData/", 
  "COVID-19/master/csse_covid_19_data/", "csse_covid_19_time_series/", 
  "time_series_covid19_confirmed_global.csv", sep = "")

jhu_deaths <- paste("https://raw.githubusercontent.com/CSSEGISandData/", 
  "COVID-19/master/csse_covid_19_data/", "csse_covid_19_time_series/", 
  "time_series_covid19_deaths_global.csv", sep = "")

download.file(url = jhu_confirmed, destfile = "data/jhu_confirmed.csv")
download.file(url = jhu_deaths, destfile = "data/jhu_deaths.csv")

cases <- read_csv(jhu_confirmed) %>% rename(province = "Province/State", 
  country = "Country/Region") %>% pivot_longer(-c(province, 
  country, Lat, Long), names_to = "Date", values_to = "cumulative_cases") %>% 
  mutate(Date = mdy(Date)) %>%
  mutate(cases = c(0, diff(cumulative_cases))) %>% 
  mutate(cases = ifelse(cases < 0, 0, cases )) %>% 
  ungroup()

cases <- read_csv(jhu_confirmed) %>% rename(province = "Province/State", 
  country = "Country/Region") %>% pivot_longer(-c(province, 
  country, Lat, Long), names_to = "Date", values_to = "cumulative_cases") %>% 
  mutate(Date = mdy(Date)) %>%
  
  # cumultaive cases by province and country
  group_by(country,province) %>% 
  mutate(cases = cumulative_cases - lag(cumulative_cases)) %>% 
  group_by(country, Date) %>%
  mutate(country_cum_cases = sum(cumulative_cases)) %>% 
  ungroup() %>% 
  mutate(country_cases = country_cum_cases - lag(country_cum_cases)) %>% 
  
  # clean up the NA and negative values
  mutate(country_cases = ifelse(country_cases < 0, 0, country_cases)) %>% 
  mutate(cases = ifelse(is.na(cases), 0, cases ))

deaths <- read_csv(jhu_deaths) %>% rename(province = "Province/State", 
  country = "Country/Region") %>% pivot_longer(-c(province, 
  country, Lat, Long), names_to = "Date", values_to = "cumulative_deaths") %>% 
  mutate(Date = mdy(Date)) %>%
  
  # cumultaive deaths by province and country
  group_by(country,province) %>% 
  mutate(deaths = cumulative_deaths - lag(cumulative_deaths)) %>% 
  group_by(country, Date) %>%
  mutate(country_cum_deaths = sum(cumulative_deaths)) %>% 
  ungroup() %>% 
  mutate(country_deaths = country_cum_deaths - lag(country_cum_deaths)) %>% 
  
  # clean up the NA and negative values
  mutate(country_deaths = ifelse(country_deaths < 0, 0, country_deaths)) %>% 
  mutate(deaths = ifelse(is.na(deaths), 0, deaths ))

coronavirus <- left_join(cases, deaths)

latest <- coronavirus %>% filter(Date == max(Date))
nz <- coronavirus %>% filter(country == "New Zealand")
```

Summary
=======================================================================

Row {data-width=400}
-----------------------------------------------------------------------

### confirmed {.value-box}

```{r}

valueBox(
  value = paste(format(max(nz$cumulative_cases), big.mark = ","), "", sep = " "),
  caption = "Total confirmed cases",
  icon = "fas fa-user-md",
  color = confirmed_color
)
```


### active {.value-box}

```{r}
valueBox(
  value = paste(format(max(nz$cumulative_deaths), big.mark = ","), " (",
    round(100 * sum(df$unrecovered, na.rm = TRUE) / sum(df$confirmed), 1),
    "%)",
    sep = ""
  ),
  caption = "Active cases (% of total cases)", icon = "fas fa-ambulance",
  color = active_color
)
```

### death {.value-box}

```{r}

valueBox(
  value = paste(format(max(nz$cumulative_deaths), big.mark = ","), "", sep = " "),
  caption = "Death cases (death rate)",
  icon = "fas fa-heart-broken",
  color = death_color
)
```


Row
-----------------------------------------------------------------------

### **Daily cumulative cases by type** (New Zealand only)
    
```{r}

# plot nz growth
who = "New Zealand"
p1 <- coronavirus %>% filter(country == who, cumulative_cases > 0) %>% 
  ggplot(aes(x = Date, y = country_cum_cases)) +
  geom_point() +
  geom_line()
p1

p2 <- coronavirus %>% filter(country == who) %>% 
  ggplot(aes(x = Date, y = country_cases)) +
  geom_bar(stat="identity")
#p2

```

Comparison
=======================================================================


Column {data-width=400}
-------------------------------------


### **Daily new cases**
    
```{r}

#----------------------------------------
# Plotting the data

p2
```
 
### **Cases distribution by type**

```{r daily_summary, eval = F}

```


Map
=======================================================================

### **World map of cases** (*use + and - icons to zoom in/out*)

```{r, eval = f}
# make a ma
library(leaflet)
library(leafpop)

map_object %>%
  addLayersControl(
    overlayGroups = names(cv_data_for_plot.split),
    options = layersControlOptions(collapsed = FALSE)
  )
```





About
=======================================================================

**The Coronavirus Dashboard: the case of New Zealand**

This Coronavirus dashboard: the case of New Zealand provides an overview of the 2019 Novel Coronavirus COVID-19 (2019-nCoV) epidemic for New Zealand. This dashboard is built with R using the R Makrdown framework and was adapted from this [dashboard](https://ramikrispin.github.io/coronavirus_dashboard/){target="_blank"} by Rami Krispin.

**Code**

The code behind this dashboard is available on [GitHub](https://github.com/AntoineSoetewey/coronavirus_dashboard){target="_blank"}.

**Data**

The input data for this dashboard is the dataset available from the [`{coronavirus}`](https://github.com/RamiKrispin/coronavirus){target="_blank"} R package. Make sure to download the development version of the package to have the latest data:

```
install.packages("devtools")
devtools::install_github("RamiKrispin/coronavirus")
```

The data and dashboard are refreshed on a daily basis.

The raw data is pulled from the Johns Hopkins University Center for Systems Science and Engineering (JHU CCSE) Coronavirus [repository](https://github.com/RamiKrispin/coronavirus-csv){target="_blank"}.

**Contact**

For any question or feedback, you can [contact me](https://www.statsandr.com/contact/). More information about this dashboard can be found in this [article](https://www.statsandr.com/blog/how-to-create-a-simple-coronavirus-dashboard-specific-to-your-country-in-r/).

**Update**

The data is as of `r format(max(coronavirus$date), "%A %B %d, %Y")` and the dashboard has been updated on `r format(Sys.time(), "%A %B %d, %Y")`.



*Go back to [www.statsandr.com](https://www.statsandr.com/) (blog) or [www.antoinesoetewey.com](https://www.antoinesoetewey.com/) (personal website)*.