---
title: "COVID19 - New Zealand"
author: "Matt Bixley"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    # social: ["facebook", "twitter", "linkedin"]
    source_code: embed
    vertical_layout: fill
---

```{r setup, include=FALSE}
#------------------ Packages ------------------
library(flexdashboard)
# install.packages("devtools")
#devtools::install_github("RamiKrispin/coronavirus")
library(tidyverse)
library(coronavirus)
data(coronavirus)
update_datasets()
# View(coronavirus)

#------------------ Parameters ------------------
# Set colors
# https://www.w3.org/TR/css-color-3/#svg-color
confirmed_color <- "purple"
active_color <- "#1f77b4"
recovered_color <- "forestgreen"
death_color <- "red"
#------------------ Data ------------------
jhu_confirmed <- paste("https://raw.githubusercontent.com/CSSEGISandData/", 
  "COVID-19/master/csse_covid_19_data/", "csse_covid_19_time_series/", 
  "time_series_covid19_confirmed_global.csv", sep = "")

jhu_deaths <- paste("https://raw.githubusercontent.com/CSSEGISandData/", 
  "COVID-19/master/csse_covid_19_data/", "csse_covid_19_time_series/", 
  "time_series_covid19_deaths_global.csv", sep = "")

download.file(url = jhu_confirmed, destfile = "data/jhu_confirmed.csv")
download.file(url = jhu_deaths, destfile = "data/jhu_deaths.csv")

jhu_c <- read_csv(jhu_confirmed)
jhu_d <- read_csv(jhu_deaths)

cases <- jhu_c %>% rename(province = "Province/State", 
  country = "Country/Region") %>% pivot_longer(-c(province, 
  country, Lat, Long), names_to = "Date", values_to = "cumulative_cases") %>% 
  mutate(cases = c(0, diff(cumulative_cases))) %>% 
  mutate(cases = ifelse(cases < 0, 0, cases )) %>% 
  ungroup() #select(-c(country_region, Lat, Long, cumulative_cases))

deaths <- jhu_d %>% rename(province = "Province/State", 
  country = "Country/Region") %>% pivot_longer(-c(province, 
  country, Lat, Long), names_to = "Date", values_to = "cumulative_deaths") %>% 
  mutate(deaths = c(0, diff(cumulative_deaths))) %>% 
  mutate(deaths = ifelse(deaths < 0, 0, deaths )) %>% 
  ungroup() #select(-c(country_region, Lat, Long, cumulative_cases))

coronavirus2 <- left_join(cases, deaths)

latest <- coronavirus2 %>% filter(Date == max(Date))
nz <- coronavirus2 %>% filter(country == "New Zealand")
```

Summary
=======================================================================

Row {data-width=400}
-----------------------------------------------------------------------

### confirmed {.value-box}

```{r}

valueBox(
  value = paste(format(max(nz$cumulative_cases), big.mark = ","), "", sep = " "),
  caption = "Total confirmed cases",
  icon = "fas fa-user-md",
  color = confirmed_color
)
```


### active {.value-box}

```{r}
valueBox(
  value = paste(format(max(nz$cumulative_deaths), big.mark = ","), " (",
    round(100 * sum(df$unrecovered, na.rm = TRUE) / sum(df$confirmed), 1),
    "%)",
    sep = ""
  ),
  caption = "Active cases (% of total cases)", icon = "fas fa-ambulance",
  color = active_color
)
```

### death {.value-box}

```{r}

valueBox(
  value = paste(format(max(nz$cumulative_deaths), big.mark = ","), "", sep = " "),
  caption = "Death cases (death rate)",
  icon = "fas fa-heart-broken",
  color = death_color
)
```


Row
-----------------------------------------------------------------------

### **Daily cumulative cases by type** (New Zealand only)
    
```{r}

# plot nz growth


plotly::plot_ly(data = nz) %>%
  plotly::add_trace(
    x = ~Date,
    y = ~cumulative_cases,
    type = "scatter",
    mode = "lines+markers",
    name = "Active",
    line = list(color = active_color),
    marker = list(color = active_color)
  ) %>%
  plotly::add_trace(
    x = ~Date,
    y = ~cumulative_deaths,
    type = "scatter",
    mode = "lines+markers",
    name = "Death",
    line = list(color = death_color),
    marker = list(color = death_color)
  ) %>%
  plotly::add_annotations(
    x = as.Date("2020-02-28"),
    y = 1,
    text = paste("First case"),
    xref = "x",
    yref = "y",
    arrowhead = 5,
    arrowhead = 3,
    arrowsize = 1,
    showarrow = TRUE,
    ax = -10,
    ay = -90
  ) %>%
  plotly::add_annotations(
    x = as.Date("2020-03-14"),
    y = 3,
    text = paste("Flight Restrictions"),
    xref = "x",
    yref = "y",
    arrowhead = 5,
    arrowhead = 3,
    arrowsize = 1,
    showarrow = TRUE,
    ax = -90,
    ay = -90
  ) %>%
  plotly::add_annotations(
    x = as.Date("2020-03-23"),
    y = 14,
    text = paste(
      "Announce Lockdown"
    ),
    xref = "x",
    yref = "y",
    arrowhead = 5,
    arrowhead = 3,
    arrowsize = 1,
    showarrow = TRUE,
    ax = -10,
    ay = -90
  ) %>%
  plotly::layout(
    title = "",
    yaxis = list(title = "Cumulative number of cases"),
    xaxis = list(title = "Date"),
    legend = list(x = 0.1, y = 0.9),
    hovermode = "compare"
  )
```

Comparison
=======================================================================


Column {data-width=400}
-------------------------------------


### **Daily new cases**
    
```{r}
daily_confirmed <- coronavirus %>%
  filter(type == "confirmed") %>%
  filter(date >= "2020-02-29") %>%
  mutate(country = Country.Region) %>%
  group_by(date, country) %>%
  summarise(total = sum(cases)) %>%
  ungroup() %>%
  pivot_wider(names_from = country, values_from = total)

#----------------------------------------
# Plotting the data

daily_confirmed %>%
  plotly::plot_ly() %>%
  plotly::add_trace(
    x = ~ date,
    y = ~ Belgium,
    type = "scatter",
    mode = "lines+markers",
    name = "New Zealand"
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~France,
    type = "scatter",
    mode = "lines+markers",
    name = "France"
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~Spain,
    type = "scatter",
    mode = "lines+markers",
    name = "Spain"
  ) %>%
  plotly::add_trace(
    x = ~date,
    y = ~Italy,
    type = "scatter",
    mode = "lines+markers",
    name = "Italy"
  ) %>%
  plotly::layout(
    title = "",
    legend = list(x = 0.1, y = 0.9),
    yaxis = list(title = "Number of new cases"),
    xaxis = list(title = "Date"),
    # paper_bgcolor = "black",
    # plot_bgcolor = "black",
    # font = list(color = 'white'),
    hovermode = "compare",
    margin = list(
      # l = 60,
      # r = 40,
      b = 10,
      t = 10,
      pad = 2
    )
  )
```
 
### **Cases distribution by type**

```{r daily_summary, eval = F}
df_EU <- coronavirus %>%
  # filter(date == max(date)) %>%
  filter(Country.Region == "New Zealand" |
    Country.Region == "France" |
    Country.Region == "Italy" |
    Country.Region == "Spain") %>%
  group_by(Country.Region, type) %>%
  summarise(total = sum(cases)) %>%
  pivot_wider(
    names_from = type,
    values_from = total
  ) %>%
  mutate(unrecovered = confirmed - ifelse(is.na(recovered), 0, recovered) - ifelse(is.na(death), 0, death)) %>%
  arrange(confirmed) %>%
  ungroup() %>%
  mutate(country = if_else(Country.Region == "United Arab Emirates", "UAE", Country.Region)) %>%
  mutate(country = if_else(country == "Mainland China", "China", country)) %>%
  mutate(country = if_else(country == "North Macedonia", "N.Macedonia", country)) %>%
  mutate(country = trimws(country)) %>%
  mutate(country = factor(country, levels = country))

plotly::plot_ly(
  data = df_EU,
  x = ~country,
  y = ~unrecovered,
  # text =  ~ confirmed,
  # textposition = 'auto',
  type = "bar",
  name = "Active",
  marker = list(color = active_color)
) %>%
  plotly::add_trace(
    y = ~death,
    # text =  ~ death,
    # textposition = 'auto',
    name = "Death",
    marker = list(color = death_color)
  ) %>%
  plotly::layout(
    barmode = "stack",
    yaxis = list(title = "Total cases"),
    xaxis = list(title = ""),
    hovermode = "compare",
    margin = list(
      # l = 60,
      # r = 40,
      b = 10,
      t = 10,
      pad = 2
    )
  )
```


Map
=======================================================================

### **World map of cases** (*use + and - icons to zoom in/out*)

```{r}
# map tab added by Art Steinmetz
library(leaflet)
library(leafpop)
library(purrr)
cv_data_for_plot <- coronavirus %>%
  # filter(Country.Region == "New Zealand") %>%
  filter(cases > 0) %>%
  group_by(Country.Region, Province.State, Lat, Long, type) %>%
  summarise(cases = sum(cases)) %>%
  mutate(log_cases = 2 * log(cases)) %>%
  ungroup()
cv_data_for_plot.split <- cv_data_for_plot %>% split(cv_data_for_plot$type)
pal <- colorFactor(c("orange", "red", "green"), domain = c("confirmed", "death", "recovered"))
map_object <- leaflet() %>% addProviderTiles(providers$Stamen.Toner)
names(cv_data_for_plot.split) %>%
  purrr::walk(function(df) {
    map_object <<- map_object %>%
      addCircleMarkers(
        data = cv_data_for_plot.split[[df]],
        lng = ~Long, lat = ~Lat,
        #                 label=~as.character(cases),
        color = ~ pal(type),
        stroke = FALSE,
        fillOpacity = 0.8,
        radius = ~log_cases,
        popup = leafpop::popupTable(cv_data_for_plot.split[[df]],
          feature.id = FALSE,
          row.numbers = FALSE,
          zcol = c("type", "cases", "Country.Region", "Province.State")
        ),
        group = df,
        #                 clusterOptions = markerClusterOptions(removeOutsideVisibleBounds = F),
        labelOptions = labelOptions(
          noHide = F,
          direction = "auto"
        )
      )
  })

map_object %>%
  addLayersControl(
    overlayGroups = names(cv_data_for_plot.split),
    options = layersControlOptions(collapsed = FALSE)
  )
```





About
=======================================================================

**The Coronavirus Dashboard: the case of New Zealand**

This Coronavirus dashboard: the case of New Zealand provides an overview of the 2019 Novel Coronavirus COVID-19 (2019-nCoV) epidemic for New Zealand. This dashboard is built with R using the R Makrdown framework and was adapted from this [dashboard](https://ramikrispin.github.io/coronavirus_dashboard/){target="_blank"} by Rami Krispin.

**Code**

The code behind this dashboard is available on [GitHub](https://github.com/AntoineSoetewey/coronavirus_dashboard){target="_blank"}.

**Data**

The input data for this dashboard is the dataset available from the [`{coronavirus}`](https://github.com/RamiKrispin/coronavirus){target="_blank"} R package. Make sure to download the development version of the package to have the latest data:

```
install.packages("devtools")
devtools::install_github("RamiKrispin/coronavirus")
```

The data and dashboard are refreshed on a daily basis.

The raw data is pulled from the Johns Hopkins University Center for Systems Science and Engineering (JHU CCSE) Coronavirus [repository](https://github.com/RamiKrispin/coronavirus-csv){target="_blank"}.

**Contact**

For any question or feedback, you can [contact me](https://www.statsandr.com/contact/). More information about this dashboard can be found in this [article](https://www.statsandr.com/blog/how-to-create-a-simple-coronavirus-dashboard-specific-to-your-country-in-r/).

**Update**

The data is as of `r format(max(coronavirus$date), "%A %B %d, %Y")` and the dashboard has been updated on `r format(Sys.time(), "%A %B %d, %Y")`.



*Go back to [www.statsandr.com](https://www.statsandr.com/) (blog) or [www.antoinesoetewey.com](https://www.antoinesoetewey.com/) (personal website)*.